### 2013-05-29 papers/bprheo_r/bprheo.tex
Added new directory with revised bprheo paper
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@1991 40876441-3496-0410-a613-a2fca35b2ae2

\begin{figure}[htpb]
\includegraphics[width=0.495\textwidth]{stress_bp2.pdf}
\includegraphics[width=0.495\textwidth]{stress_vs_strain_bp2.pdf}
\caption{Apparent viscosity $\eta_{app}=\Pi_{xy}/\gd$ (normalised to $\eta$) 
of BPII versus time (top) and strain (bottom). 
For clarity the individual curves have been shifted along the time and strain axis. 
The inset in the top panel 
shows the flow curve $\bar{\Pi}_{xy}(\gd)$ and two different regimes of flow: 
regular periodic breakup and reconnecting of the disclination lines (BPII-1, open circles), 
break up of the network into a travelling helical wave (BPII-2, solid circle), 
cholesteric helix with axis in gradient direction (CHG, open squares)
and flow-aligned nematic state (FAN, solid square).
The error bars indicate the maximum and minimum stresses that occur during one cycle.}
\label{bp2-rheo}
\end{figure}

@@

\begin{figure}[htpb]
\includegraphics[width=0.495\textwidth]{stress_bp1.pdf}
\includegraphics[width=0.495\textwidth]{stress_vs_strain_bp1.pdf}
\caption{Apparent viscosity $\eta_{app}=\langle \Pi_{xy}\rangle/\dot{\gamma}$ (normalised by $\eta$) of BPI versus time (top) 
and strain (bottom). The inset shows the flow curve $\bar{\Pi}_{xy}(\gd)$. 
Depending on the configuration in steady shear flow three different regimes 
can be identified: amorphous BP network with yield stress (BPI-1, triangles), 
steady flow with recurring patterns (BPI-2, open circles), 
breakup of the disclination network (BPI-3, solid circle), 
cholesteric helix with axis in gradient direction (CHG, open squares) 
and flow-aligned nematic state (FAN, solid square). 
The error bars represent the minimum and maximum shear stress 
during one cycle. For clarity the individual curves have been shifted along
the time and strain axis.}
\label{bp1-rheo}
\end{figure}

>>>>

\begin{figure}[htpb]
\includegraphics[width=0.495\textwidth]{flowcurve_bp2.pdf}\\
\includegraphics[width=0.495\textwidth]{app_visc_strain_bp2_a.pdf}\\
\includegraphics[width=0.495\textwidth]{app_visc_strain_bp2_b.pdf}\\
\caption{Apparent viscosity $\eta_{app}=\Pi_{xy}/\gd$ (normalised to $\eta$) 
of BPII versus time (top) and strain (bottom). 
For clarity the individual curves have been shifted along the time and strain axis. 
The inset in the top panel 
shows the flow curve $\bar{\Pi}_{xy}(\gd)$ and two different regimes of flow: 
regular periodic breakup and reconnecting of the disclination lines (BPII-1, open circles), 
break up of the network into a travelling helical wave (BPII-2, solid circle), 
cholesteric helix with axis in gradient direction (CHG, open squares)
and flow-aligned nematic state (FAN, solid square).
The error bars indicate the maximum and minimum stresses that occur during one cycle.}
\label{bp2-rheo}
\end{figure}

@@

\begin{figure}[htpb]
\includegraphics[width=0.495\textwidth]{flowcurve_bp1.pdf}\\
\includegraphics[width=0.495\textwidth]{app_visc_strain_bp1_a.pdf}\\
\includegraphics[width=0.495\textwidth]{app_visc_strain_bp1_b.pdf}\\
\includegraphics[width=0.495\textwidth]{app_visc_strain_bp1_c.pdf}
\caption{Apparent viscosity $\eta_{app}=\langle \Pi_{xy}\rangle/\dot{\gamma}$ (normalised by $\eta$) of BPI versus time (top) 
and strain (bottom). The inset shows the flow curve $\bar{\Pi}_{xy}(\gd)$. 
Depending on the configuration in steady shear flow three different regimes 
can be identified: amorphous BP network with yield stress (BPI-1, triangles), 
steady flow with recurring patterns (BPI-2, open circles), 
breakup of the disclination network (BPI-3, solid circle), 
cholesteric helix with axis in gradient direction (CHG, open squares) 
and flow-aligned nematic state (FAN, solid square). 
The error bars represent the minimum and maximum shear stress 
during one cycle. For clarity the individual curves have been shifted along
the time and strain axis.}
\label{bp1-rheo}
\end{figure}
